Improving the modelling of tempo and phoneme duration

### 2017-04-05 Paper/Paper_v1.tex
pictures

\subsection{M5P}
The M5P model tree is a decision tree based on the M5 algorithm introduced by Quinlan (1992). It

>>>>

\subsection{M5P}
The M5P model tree \cite{Witten2011} is a decision tree based on the M5 algorithm introduced by Quinlan (1992). It builds a usual classification tree out of the attributes, and retrieves a linear regression model in each leaf out of the attributes contained in that specific subtree.
